---
title: "formative-ex1"
author: '202160196'
date: "2024-10-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Netflix Movies & TV Series Data

We will be using Tidyverse package to transform the Netflix dataset in order to analyze high-quality content on Netflix. This dataset includes basic information on titles as well as IMDb data like ratings and vote counts. The data has been downloaded in late October 2024 from Kaggle and the current version of the dataset was last updated in October 2024. To access the download source see <https://www.kaggle.com/datasets/octopusteam/full-netflix-dataset>.

## Loading Packages

```{r}
#Loading the package
library(tidyverse)
```

## High-quality Content on Netflix

We will first be filtering out any rows where the "url" column is blank or missing, ensuring the dataset only includes entries that have valid links to their corresponding Netflix pages for further information.

Then, we will filter the dataset to show only movies and tv shows with an IMDb rating of 8 or above and votes of , focusing on high-quality content entries.

```{r}
#Loading the Netflix dataset
netflix_data <- read.csv("/Users/tiffanylu/local/formative-ex1/netflix_data.csv")
head(netflix_data)

#Transforming dataset into tibbles
netflix_data <- as_tibble(netflix_data)
head(netflix_data)

#Transformation 1.1: Remove rows with missing "url" 
netflix_clean <- netflix_data %>%
  filter(url != "") #citation: @suzan.rbind.io
print(netflix_clean)

#Transformation 1.2: Filter for entries with with rating of 8 or above
netflix_high_quality <- netflix_clean %>%
  filter(imdbAverageRating == 8 | imdbAverageRating > 8)
print(netflix_high_quality)

```

## Organizing Data by Release Year

To create an organized summary of Netflix content by year we will group the dataset by "release_year". For each release year, we calculate the average IMDb rating and vote count, allowing us to identify years with the highest quality content.

```{r}
#Transformation 2: Group by release year and summarize data
summarize_release_year <- netflix_high_quality %>%
  group_by(releaseYear) %>%
  summarise(
    avg_imdb_rating = mean(imdbAverageRating, na.rm = TRUE),
    avg_votes = mean(imdbNumVotes, na.rm = TRUE)) %>%
  arrange(desc(releaseYear)) #citation: @dtplyr

print(summarize_release_year)



```
